Whole-body connectome of a segmented annelid larva

### 2024-10-23 Manuscript.qmd
Figures: add a-p d-v arrows to all figures

@@

```{r, out.width = "100%", fig.cap="**Figure 3—figure supplement 1. Major cell classes in the three-day-old *Platynereis* larva.** Morphological rendering of (A) all cells coloured by germ layer, (B) glia cells, (C) pigment cells, (D) ciliary band cells, (E) gland cells, (F) muscle cells, (G) dividing cells, (H) acicular and chaetal follicle cells, (I) developing cells of the neuroectoderm, (J) yolk and yolk blanket cells (K) aciculoblasts and chaetoblasts, (L) proto- and metanephridia, (M) epithelial cells, (N) coelothelial cells and (O) cells of the stomodeum and hindgut. In all panels all other cells of the body are shown in transparent cyan and the yolk in grey for reference. Each panel shows a ventral (left) and a left view (right). Left views only show cells on the left body side. "}
#| echo: false
knitr::include_graphics("Figures/Figure3_fig_suppl1.png")
```

@@

```{r, out.width = "100%", fig.cap="**Figure 10—figure supplement 1. Head descending and decussating neurons.** (A) Morphological rendering of the neurites of head desending (blue) and decussationg (yellow) neurons. (B) Names of head descending and decussationg cell types. (C) Postsynaptic sites of head descending and decussating neurons. (D) Presynaptic sites of head descending and decussating neurons. (E) Postsynaptic targets of head descending and decussating neurons. (F) Distribution of the neurites of head descending and decussating neurons in the VNC. Cross section at the position of the thin line in (E). (G) Neurites of the postsynaptic targets of head descending and decussating neurons in the VNC. Cross section at the position of the thin line in (E). (H-I) Postsynaptic (red) and presynaptic (blue) sites of head decussating neurons in anterior (H) and ventral (I) view. (J) Mean radial density of postsynapses and presynapses in head decussating neurons. (K-L) Postsynaptic (red) and presynaptic (blue) sites of head descending neurons in anterior (K) and ventral (L) view. (M) Mean radial density of postsynapses and presynapses in head descending neurons. <br> Figure 10—figure supplement 1—source data 1. Source data for panels (J, M). "}
#| echo: false
knitr::include_graphics("Figures/Figure10_fig_suppl1.png")
```

>>>>

**Quantitative analysis of neuron morphologies**

For quantitative neuroanatomy, we used functions of CATMAID as implemented in the catmaid (catmaid-package {catmaid}: R access to the API for the CATMAID web image annotation tool) and nat (nat-package {nat}: Analyse 3D biological image data especially neurons) packages. For morphological rendering and quantititave analysis, skeletons were first smoothed with the smooth_neuron function (smooth_neuron {nat}: Smooth the 3D coordinates of a neuron skeleton) with a sigma of 6000 nm.
Neuronal cable length was calculated on trimmed skeletons. Each twig shorter than 2 mm was removed with the prune_twigs {nat} function. Cable length then gives the length of the trimmed skeletons in microns (Figure1_fig_suppl2.R code in the code repository).
For Sholl analysis, we used the sholl_analysis function (sholl_analysis {nat}: Perform a Sholl analysis on neuron skeletons) on untrimmed, smoothed skeletons.
The radial density of input and output synapses was calculated in the CATMAID web interface and the data were saved as .csv and plotted in R (Figure1.R code).

@@

```{r, out.width = "100%", fig.cap="**Figure 3—figure supplement 1. Major cell classes in the three-day-old *Platynereis* larva.** Morphological rendering of (A) all cells coloured by germ layer, (B) glia cells, (C) pigment cells, (D) ciliary band cells, (E) gland cells, (F) muscle cells, (G) dividing cells, (H) acicular and chaetal follicle cells, (I) developing cells of the neuroectoderm, (J) yolk and yolk blanket cells (K) aciculoblasts and chaetoblasts, (L) proto- and metanephridia, (M) epithelial cells, (N) coelothelial cells and (O) cells of the stomodeum and hindgut. In all panels all other cells of the body are shown in transparent cyan and the yolk in grey for reference. Each panel shows a ventral (left panel) and a left-side view (right panel). The left-side views only show cells on the left body side. "}
#| echo: false
knitr::include_graphics("Figures/Figure3_fig_suppl1.png")
```

@@

```{r, out.width = "100%", fig.cap="**Figure 10—figure supplement 1. Head descending and decussating neurons.** (A) Morphological rendering of the neurites of head desending (blue) and decussating (yellow) neurons. (B) Names of head descending and decussating cell types. (C) Postsynaptic sites of head descending and decussating neurons. (D) Presynaptic sites of head descending and decussating neurons. (E) Postsynaptic targets of head descending and decussating neurons. (F) Distribution of the neurites of head descending and decussating neurons in the VNC. Cross section at the position of the thin line in (E). (G) Neurites of the postsynaptic targets of head descending and decussating neurons in the VNC. Cross section at the position of the thin line in (E). (H-I) Postsynaptic (red) and presynaptic (blue) sites of head decussating neurons in anterior (H) and ventral (I) view. (J) Mean radial density of postsynapses and presynapses in head decussating neurons. (K-L) Postsynaptic (red) and presynaptic (blue) sites of head descending neurons in anterior (K) and ventral (L) view. (M) Mean radial density of postsynapses and presynapses in head descending neurons. <br> Figure 10—figure supplement 1—source data 1. Source data for panels (J, M). "}
#| echo: false
knitr::include_graphics("Figures/Figure10_fig_suppl1.png")
```
